Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2023-11-09 revisions.qmd
add new files

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
---

@@

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
crossref:
  custom: 
    - kind: float # crossreferenceable elements with captions are `float`
      prefix: Supplementary Figure # used as the prefix for reference in output ("In Figure 1, ..")
      name: Supplementary Figure # used as the prefix for captions ("Figure 1: ..")
      ref-type: sfig # used as the prefix for the reference identifier ("In @fig-1, ...")
---

@@

### Supplementary Information

```{r, vaginalsex}
